Milk intake and risk of mortality risk

### 2020-06-12 Paperfolder/Paperfolder.Rmd
update template confirmed

---
title: Milk intake and risk of mortality risk 
author:
  - name: Chaochen Wang
    affil: 1,*
    orcid: 0000-0001-5533-1497
  - name: Hiroshi Yatsuya
    affil: 2 
    orcid: 0000-0002-6220-9251
  - name: Yingsong Lin
    affil: 1
    orcid: 0000-0003-0214-3649
  - name: Shogo Kikuchi
    affil: 1
    orcid: 0000-0001-9499-9668
  - name: Tae Sasakabe 
    affil: 1 
    orcid: 0000-0002-7417-5693
  - name: Sayo Kawai
    affil: 1
    orcid: 0000-0002-5156-4880
  - name: Hiroyasu Iso
    affil: 3
    orcid: 0000-0002-9241-7289 
  - name: Akiko Tamakoshi
    affil: 4
    orcid: 0000-0002-9761-3879 
affiliation:
  - num: 1
    address: |
      Department of Public Health, Aichi Medical University School of Medicine, Nagakute, Japan
#    email: chaochen@wangcc.me
  - num: 2
    address: |
      Departmet of Public Health, Fujita Health University School of Medicine, Toyoake, Japan
  - num: 3
    address: |
      Public Health, Department of Social Medicine, Osaka University Graduate School of Medicine, Osaka, Japan
  - num: 4
    address: |
      Department of Public Health, Faculty of Medicine, Hokkaido University, Sapporo, Japan
#    email: yatsuya@gmail.com
# firstnote to eighthnote
# firstnote: |
#   Current address: Updated affiliation
# secondnote: |
#   These authors contributed equally to this work.
correspondence: |
  Email.: chaochen@wangcc.me; Tel.: +81-561-62-3311. Department of Public Health, Aichi Medical University School of Medicine, 1-1 Yazakokarimata, Nagakute, Aichi, 480-1195, Japan (C.W.)
journal: nutrients
type: article
status: submit
bibliography: mybibfile.bib
# appendix: appendix.tex
# simplesummary: |
#  A Simple summary goes here.
abstract: |
  A single paragraph of about 200 words maximum. For research articles, 
  abstracts should give a pertinent overview of the work. We strongly encourage
  authors to use the following style of structured abstracts, but without 
  headings: 1) Background: Place the question addressed in a broad context and
  highlight the purpose of the study; 2) Methods: Describe briefly the main
  methods or treatments applied; 3) Results: Summarize the article's main 
  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
  The abstract should be an objective representation of the article, it must not 
  contain results which are not presented and substantiated in the main text and 
  should not exaggerate the main conclusions.
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.''
conflictsofinterest: |
  The authors declare no conflict of interest. The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, an in the decision to publish the results.
# sampleavailability: |
#   Samples of the compounds ...... are available from the authors.
abbreviations:
  - short: MDPI
    long: Multidisciplinary Digital Publishing Institute
  - short: DOAJ
    long: Directory of open access journals
  - short: TLA
    long: Three letter acronym
  - short: LD 
    long: linear dichroism
output: rticles::mdpi_article
---

@@

The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper [@bertrand-krajewski_distribution_1998; @leutnant_stormwater_2016]. And now citing a book reference @gujer_systems_2008. Please use the command [@leutnant_stormwater_2016] for the following MDPI journals, which use author-date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences.

@@

Materials and Methods should be described with sufficient details to allow others to replicate and build on published results. Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers. Please disclose at the submission stage any restrictions on the availability of materials or information. New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.

Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers. If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review. They must be provided prior to publication.

Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.

@@

This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.

@@

Subsection text here.

@@

Bulleted lists look like this:

* First bullet
* Second bullet
* Third bullet

Numbered lists can be added as follows:

1. First item
2. Second item
3. Third item

The text continues here.

All figures and tables should be cited in the main text as Figure 1, Table 1, etc.

\begin{figure}[H]
\centering
\includegraphics[width=3 cm]{logo-mdpi}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}

@@

This is an example of an equation:

\begin{equation}
\mathbb{S}
\end{equation}
<!-- If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph. -->

<!-- Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows: -->
Example of a theorem:
\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

@@

Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

@@

This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

>>>>

---
title: Milk intake and risk of mortality risk 
author:
  - name: Chaochen Wang
    affil: 1,*
    orcid: 0000-0001-5533-1497
  - name: Hiroshi Yatsuya
    affil: 2 
    orcid: 0000-0002-6220-9251
  - name: Yingsong Lin
    affil: 1
    orcid: 0000-0003-0214-3649
  - name: Tae Sasakabe 
    affil: 1 
    orcid: 0000-0002-7417-5693
  - name: Sayo Kawai
    affil: 1
    orcid: 0000-0002-5156-4880
  - name: Shogo Kikuchi
    affil: 1
    orcid: 0000-0001-9499-9668
  - name: Hiroyasu Iso
    affil: 3
    orcid: 0000-0002-9241-7289 
  - name: Akiko Tamakoshi
    affil: 4
    orcid: 0000-0002-9761-3879 
affiliation:
  - num: 1
    address: |
      Department of Public Health, Aichi Medical University School of Medicine, Nagakute, Japan
#    email: chaochen@wangcc.me
  - num: 2
    address: |
      Departmet of Public Health, Fujita Health University School of Medicine, Toyoake, Japan
  - num: 3
    address: |
      Public Health, Department of Social Medicine, Osaka University Graduate School of Medicine, Osaka, Japan
  - num: 4
    address: |
      Department of Public Health, Faculty of Medicine, Hokkaido University, Sapporo, Japan
#    email: yatsuya@gmail.com
# firstnote to eighthnote
# firstnote: |
#   Current address: Updated affiliation
# secondnote: |
#   These authors contributed equally to this work.
correspondence: |
  Email.: chaochen@wangcc.me; Tel.: +81-561-62-3311. Department of Public Health, Aichi Medical University School of Medicine, 1-1 Yazakokarimata, Nagakute, Aichi, 480-1195, Japan (C.W.)
journal: nutrients
type: article
status: submit
bibliography: mybibfile.bib
# appendix: appendix.tex
# simplesummary: |
#  A Simple summary goes here.
abstract: |
  A single paragraph of about 200 words maximum. For research articles, 
  abstracts should give a pertinent overview of the work. We strongly encourage
  authors to use the following style of structured abstracts, but without 
  headings: 1) Background: Place the question addressed in a broad context and
  highlight the purpose of the study; 2) Methods: Describe briefly the main
  methods or treatments applied; 3) Results: Summarize the article's main 
  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
  The abstract should be an objective representation of the article, it must not 
  contain results which are not presented and substantiated in the main text and 
  should not exaggerate the main conclusions.
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.''
conflictsofinterest: |
  The authors declare no conflict of interest. The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, an in the decision to publish the results.
# sampleavailability: |
#   Samples of the compounds ...... are available from the authors.
abbreviations:
  - short: JACC
    long: Japan Collaborative Cohort 
  - short: DOAJ
    long: Directory of open access journals
  - short: TLA
    long: Three letter acronym
  - short: LD 
    long: linear dichroism
output: rticles::mdpi_article
---

@@

<!-- The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper [@bertrand-krajewski_distribution_1998; @leutnant_stormwater_2016]. And now citing a book reference @gujer_systems_2008. Please use the command [@leutnant_stormwater_2016] for the following MDPI journals, which use author-date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences. -->

@@

<!-- Materials and Methods should be described with sufficient details to allow others to replicate and build on published results. Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers. Please disclose at the submission stage any restrictions on the availability of materials or information. New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited. -->

<!-- Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers. If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review. They must be provided prior to publication. -->

<!-- Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code. -->

@@

<!-- This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn. -->

@@

<!-- Subsection text here. -->

@@

<!-- Bulleted lists look like this: -->

<!-- * First bullet -->
<!-- * Second bullet -->
<!-- * Third bullet -->

<!-- Numbered lists can be added as follows: -->

<!-- 1. First item -->
<!-- 2. Second item -->
<!-- 3. Third item -->

<!-- The text continues here. -->

<!-- All figures and tables should be cited in the main text as Figure 1, Table 1, etc. -->

<!-- \begin{figure}[H] -->
<!-- \centering -->
<!-- \includegraphics[width=3 cm]{logo-mdpi} -->
<!-- \caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.} -->
<!-- \end{figure} -->

@@

<!-- This is an example of an equation: -->

<!-- \begin{equation} -->
<!-- \mathbb{S} -->
<!-- \end{equation} -->
<!-- If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph. -->

<!-- Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows: -->
<!-- Example of a theorem: -->
<!-- \begin{Theorem} -->
<!-- Example text of a theorem. -->
<!-- \end{Theorem} -->

<!-- The text continues here. Proofs must be formatted as follows: -->

@@

<!-- Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted. -->

@@

<!-- This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex. -->

### 2020-06-12 Paperfolder/Paperfolder.tex
update template confirmed

% Authors, for the paper (add full first names)
\Author{Chaochen
Wang$^{1,*}$\href{https://orcid.org/0000-0001-5533-1497}{\orcidicon}, Hiroshi
Yatsuya$^{2}$\href{https://orcid.org/0000-0002-6220-9251}{\orcidicon}, Yingsong
Lin$^{1}$\href{https://orcid.org/0000-0003-0214-3649}{\orcidicon}, Shogo
Kikuchi$^{1}$\href{https://orcid.org/0000-0001-9499-9668}{\orcidicon}, Tae
Sasakabe$^{1}$\href{https://orcid.org/0000-0002-7417-5693}{\orcidicon}, Sayo
Kawai$^{1}$\href{https://orcid.org/0000-0002-5156-4880}{\orcidicon}, Hiroyasu
Iso$^{3}$\href{https://orcid.org/0000-0002-9241-7289}{\orcidicon}, Akiko
Tamakoshi$^{4}$\href{https://orcid.org/0000-0002-9761-3879}{\orcidicon}}

% Authors, for metadata in PDF
\AuthorNames{Chaochen Wang, Hiroshi Yatsuya, Yingsong Lin, Shogo
Kikuchi, Tae Sasakabe, Sayo Kawai, Hiroyasu Iso, Akiko Tamakoshi}

@@

The introduction should briefly place the study in a broad context and
highlight why it is important. It should define the purpose of the work
and its significance. The current state of the research field should be
reviewed carefully and key publications cited. Please highlight
controversial and diverging hypotheses when necessary. Finally, briefly
mention the main aim of the work and highlight the principal
conclusions. As far as possible, please keep the introduction
comprehensible to scientists outside your particular field of research.
Citing a journal paper
\citep{bertrand-krajewski_distribution_1998, leutnant_stormwater_2016}.
And now citing a book reference \citet{gujer_systems_2008}. Please use
the command \citep{leutnant_stormwater_2016} for the following MDPI
journals, which use author-date citation: Administrative Sciences, Arts,
Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws,
Religions, Risks, Social Sciences.

@@

Materials and Methods should be described with sufficient details to
allow others to replicate and build on published results. Please note
that publication of your manuscript implicates that you must make all
materials, data, computer code, and protocols associated with the
publication available to readers. Please disclose at the submission
stage any restrictions on the availability of materials or information.
New methods and protocols should be described in detail while
well-established methods can be briefly described and appropriately
cited.

Research manuscripts reporting large datasets that are deposited in a
publicly available database should specify where the data have been
deposited and provide the relevant accession numbers. If the accession
numbers have not yet been obtained at the time of submission, please
state that they will be provided during review. They must be provided
prior to publication.

Interventionary studies involving animals or humans, and other studies
require ethical approval must list the authority that provided approval
and the corresponding ethical approval code.

@@

This section may be divided by subheadings. It should provide a concise
and precise description of the experimental results, their
interpretation as well as the experimental conclusions that can be
drawn.

@@

Subsection text here.

@@

Bulleted lists look like this:

\begin{itemize}
\tightlist
\item
  First bullet
\item
  Second bullet
\item
  Third bullet
\end{itemize}

Numbered lists can be added as follows:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  First item
\item
  Second item
\item
  Third item
\end{enumerate}

The text continues here.

All figures and tables should be cited in the main text as Figure 1,
Table 1, etc.

\begin{figure}[H]
\centering
\includegraphics[width=3 cm]{logo-mdpi}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}

@@

This is an example of an equation:

\begin{equation}
\mathbb{S}
\end{equation}

Example of a theorem:

\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

@@

\noindent
\begin{tabular}{@{}ll}
MDPI & Multidisciplinary Digital Publishing Institute \\
DOAJ & Directory of open access journals \\
TLA & Three letter acronym \\
LD & linear dichroism \\
\end{tabular}}

>>>>

% Authors, for the paper (add full first names)
\Author{Chaochen
Wang$^{1,*}$\href{https://orcid.org/0000-0001-5533-1497}{\orcidicon}, Hiroshi
Yatsuya$^{2}$\href{https://orcid.org/0000-0002-6220-9251}{\orcidicon}, Yingsong
Lin$^{1}$\href{https://orcid.org/0000-0003-0214-3649}{\orcidicon}, Tae
Sasakabe$^{1}$\href{https://orcid.org/0000-0002-7417-5693}{\orcidicon}, Sayo
Kawai$^{1}$\href{https://orcid.org/0000-0002-5156-4880}{\orcidicon}, Shogo
Kikuchi$^{1}$\href{https://orcid.org/0000-0001-9499-9668}{\orcidicon}, Hiroyasu
Iso$^{3}$\href{https://orcid.org/0000-0002-9241-7289}{\orcidicon}, Akiko
Tamakoshi$^{4}$\href{https://orcid.org/0000-0002-9761-3879}{\orcidicon}}

% Authors, for metadata in PDF
\AuthorNames{Chaochen Wang, Hiroshi Yatsuya, Yingsong Lin, Tae
Sasakabe, Sayo Kawai, Shogo Kikuchi, Hiroyasu Iso, Akiko Tamakoshi}

@@

@@

@@

@@

@@

@@

@@

\noindent
\begin{tabular}{@{}ll}
JACC & Japan Collaborative Cohort \\
DOAJ & Directory of open access journals \\
TLA & Three letter acronym \\
LD & linear dichroism \\
\end{tabular}}
